---
title: "co_unit"
author: "Siyan Pu"
date: "1/11/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(httr)
library(jsonlite)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(ggpubr)
```

airly all CO data preprocessing
```{r}
airly_cob <- read.csv("airly_co.csv", check.names = F)
airly_cob <- airly_cob %>%
  gather(sensor_id, CO, -c('Time')) %>%
  rename('date' = 'Time')
airly_cob <- airly_cob[,c(1,3,2)] 
airly_cob$sensor_id <- as.integer(airly_cob$sensor_id)

airly_coc <- read.csv("airly_co_nov.csv", check.names = F)
airly_coc <- airly_coc %>%
  gather(sensor_id, CO, -c('Time', 'mark')) %>%
  rename('date' = 'Time')
airly_coc$sensor_id <- as.integer(airly_coc$sensor_id)

airly_coc <- airly_coc %>%
  select(-mark)
airly_coc <- airly_coc[,c(1,3,2)]
```

```{r}
airly_coa <- read.csv("airly2.csv") %>%
  select(date, CO, sensor_id)
airly2 <- rbind(airly_coa, airly_cob, airly_coc)

#convert to EST time zone (before daylight saving, 7 hour difference)
airly2$time <- as.POSIXct(airly2$date, format="%Y-%m-%d %H:%M:%S", tz="CET")
airly2$time <- lubridate::with_tz(airly2$time, "EST")

airly2$day <- date(strptime(airly2$time, format="%Y-%m-%d %H:%M:%S"))
airly2$hour <- hour(strptime(airly2$time, format="%Y-%m-%d %H:%M:%S"))
airly2$dayhour <- lubridate::ymd_h(format(as.POSIXct(airly2$time,format="%Y-%m-%d %H:%M:%S"),"%Y-%m-%d %H"))
airly2$sensor_id <- as.factor(airly2$sensor_id)
```

```{r}
airly_co <- airly2 %>%
  select(time, CO, day, hour, dayhour, sensor_id) %>%
  filter(day >= '2021-09-06' & day <= '2021-11-07')

airly_co <- airly_co %>%
  filter(!is.na(CO))

airly_co$CO[airly_co$CO < 0] <- 0
```



Preprocess regulatory data and calculate hourly regulatory data
```{r}
regular_coa <- regular1 %>%
  select(time, CO, day, dayhour, Temp, RH, Pressure)

regular_cob <- regular2 %>%
  select(time, CO, day, dayhour, Temp, RH, Pressure)

regular_co <- rbind(regular_coa, regular_cob)
#nrow(regular_co %>% filter(regular_co$CO == ' C '))
regular_co$CO[regular_co$CO == ' C '] <- NA
regular_co$CO <- as.numeric(regular_co$CO, na.rm = T)
regular_co$CO[regular_co$CO < 0] <- 0

temp2 <- regular_co %>%
  group_by(dayhour) %>%
  summarise(rhourlyCO = mean(CO, na.rm = T), rTemp = mean(Temp, na.rm = T), rRH = mean(RH, na.rm = T), rPre = mean(Pressure, na.rm = T))

temp4 <- regular_co %>%
  group_by(day) %>%
  summarise(rdailyCO = mean(CO, na.rm = T), rTemp = mean(Temp, na.rm = T), rRH = mean(RH, na.rm = T), rPre = mean(Pressure, na.rm = T))
```

sensor to sensor comparison plot (daily)
```{r}
temp3 <- airly_co %>%
  group_by(day, sensor_id) %>%
  summarise(adailyCO = mean(CO, na.rm = T)) %>%
  na.omit()

#adailyCO (PPM) = adailyCO(ug/cm3)
temp3 <- merge(temp3, temp4, by = "day") %>%
  mutate(new_adailyCO = adailyCO * 8.314 * (rTemp+273.15)/(rPre*100*28.01)) %>%
  select(day, sensor_id, dailyCO = new_adailyCO)

temp4 <- temp4 %>%
  select(day, rdailyCO)
temp4$sensor_id <- 'FRM/FEM'

cod_sensortosensor <- ggplot(data = temp3, aes(x=day, y=dailyCO)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = temp4, aes(x=day, y=rdailyCO, lty="FRM/FEM"), color="black") +
  xlab("Date") +ylab(expression(paste("Daily CO [ppm]"))) + ggtitle('Before Correction')
#ggsave("cod_sensortosensor.png")

#Precision for CO
temp_pre1 <- temp3 %>%
  group_by(day) %>%
  filter(day >= '2021-09-20' & day <= '2021-11-08') %>%
  summarise(dailyCO_all = mean(dailyCO, na.rm = T))

temp_pre2 <- temp3 %>%
  group_by(day, sensor_id) %>%
  filter(day >= '2021-09-20' & day <= '2021-11-08') %>%
  summarise(dailyCO = mean(dailyCO, na.rm = T))

CO <- merge(temp_pre1, temp_pre2, by = "day", all.x = T) %>%
  mutate(diff_square = (dailyCO_all-dailyCO)**2)

M <- n_distinct(CO$sensor_id)
N <- n_distinct(CO$day)

SD <- sqrt(sum(CO$diff_square) / (M*N-1))
SD/mean(temp3$dailyCO, na.rm=T)*100
```

RMSE
```{r}
CO_rm <- merge(temp3, temp4 %>% select(-sensor_id), by = "day", all.x = T) %>%
  filter(day >= '2021-09-20' & day <= '2021-11-08') %>%
  mutate(diff_square = (rdailyCO-dailyCO)**2) %>%
  na.omit()

M <- n_distinct(CO_rm$sensor_id)
N <- n_distinct(CO_rm$day)

RMSE <- sqrt(sum(CO_rm$diff_square) / (M*N-1))
RMSE / mean(CO_rm$rdailyCO, na.rm = T) *100
temp_50daya <- temp3 %>%
    filter(day >= '2021-09-20' & day <= '2021-11-08')
temp_50dayr <- temp4 %>%
    filter(day >= '2021-09-20' & day <= '2021-11-08')
#Accuracy
100-abs(mean(temp_50daya$dailyCO, na.rm = T)-mean(temp_50dayr$rdailyCO, na.rm = T))/mean(temp_50dayr$rdailyCO, na.rm = T)*100

#Inter-sensor Variability
sensor_avg <- temp_50daya %>%
  group_by(sensor_id) %>%
  summarise(avge = mean(dailyCO, na.rm = T)) %>%
  arrange(avge)

(max(sensor_avg$avge)-min(sensor_avg$avge))/mean(sensor_avg$avge, na.rm=T)
```

  
sensor to sensor comparison plot (hourly)
```{r}
temp1 <- airly_co %>%
  group_by(dayhour, sensor_id) %>%
  summarise(ahourlyCO = mean(CO, na.rm = T)) %>%
  na.omit()

temp1 <- merge(temp1, temp2, by = "dayhour") %>%
  mutate(new_ahourlyCO = ahourlyCO * 8.314 * (rTemp+273.15)/(rPre*100*28.01)) %>%
  select(dayhour, sensor_id, hourlyCO = new_ahourlyCO)

temp2 <- temp2 %>%
  select(dayhour, hourlyCO = rhourlyCO) %>%
  group_by()
temp2$sensor_id <- 'FRM'
coh_sensortosensor <- ggplot(data = temp1, aes(x=dayhour, y=hourlyCO)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = temp2, aes(x=dayhour, y=hourlyCO, lty="FRM/FEM"), color="black") +
  xlab("Hour") +ylab(expression(paste("Hourly CO [ppm]"))) + ggtitle('Before Correction')
#ggsave("coh_sensortosensor.png")
```

obeserve diurnal pattern
```{r}
temp1 <- airly_co %>%
  group_by(dayhour, sensor_id) %>%
  summarise(ahourlyCO = mean(CO, na.rm = T)) %>%
  na.omit()

temp1 <- merge(temp1, temp2, by = "dayhour") %>%
  mutate(new_ahourlyCO = ahourlyCO * 8.314 * (rTemp+273.15)/(rPre*100*28.01),
         hour = hour(strptime(dayhour, format="%Y-%m-%d %H:%M:%S")),
         day = date(strptime(dayhour, format="%Y-%m-%d %H:%M:%S"))) %>%
  select(day, hour, sensor_id, hourlyCO = new_ahourlyCO) %>%
  group_by(hour, sensor_id) %>%
  summarise(houravgCO=mean(hourlyCO, na.rm=T))

temp3 <- temp2 %>%
  mutate(hour = hour(strptime(dayhour, format="%Y-%m-%d %H:%M:%S")),
         day = date(strptime(dayhour, format="%Y-%m-%d %H:%M:%S"))) %>%
  select(day, hour, hourlyCO = rhourlyCO) %>%
  group_by(hour) %>%
  summarise(houravgCO=mean(hourlyCO, na.rm=T))

temp3$sensor_id <- 'FRM'
coh_pattern <- ggplot(data = temp1, aes(x=hour, y=houravgCO)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = temp3, aes(x=hour, y=houravgCO, lty="FRM/FEM"), color="black")  +
  ggtitle("CO")+
  xlab("Hour") +ylab(expression(paste("Hourly CO [ppm]")))
```



```{r}
temp2 <- regular_co %>%
  group_by(dayhour) %>%
  summarise(rhourlyCO = mean(CO, na.rm = T), rTemp = mean(Temp, na.rm = T), rRH = mean(RH, na.rm = T), rPre = mean(Pressure, na.rm = T))

temp4 <- regular_co %>%
  group_by(day) %>%
  summarise(rdailyCO = mean(CO, na.rm = T), rTemp = mean(Temp, na.rm = T), rRH = mean(RH, na.rm = T), rPre = mean(Pressure, na.rm = T))
```


sensor 7160; hourly
```{r}
temp1 <- airly_co %>%
  filter(sensor_id == '7160') %>%
  group_by(dayhour) %>%
  summarise(ahourlyCO = mean(CO, na.rm = T))
CO_hour7160 <- merge(temp1, temp2, by = "dayhour") %>%
  mutate(new_ahourlyCO = ahourlyCO * 8.314 * (rTemp+273.15)/(rPre*100*28.01))
#unit of rTemp is degree celsius; unit of rPre is mbar which is 100pa
```

```{r}
CO_hour7160 %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=new_ahourlyCO, colour="airly"))+
  geom_line(aes(y=rhourlyCO, colour="FRM"))+
  xlab("Date") +ylab("hourly CO [ppm]") +
  ggtitle('Sensor 7160')

model7160hco <- lm(new_ahourlyCO ~ rhourlyCO + 1, data = CO_hour7160)
summary(model7160hco)

model7160hcoTRH <- lm(new_ahourlyCO ~ rhourlyCO + rTemp + rRH + 1, data = CO_hour7160)
summary(model7160hcoTRH)

model7160hcoT <- lm(new_ahourlyCO ~ rTemp + 1, data = CO_hour7160)
summary(model7160hcoT)
model7160hcoRH <- lm(new_ahourlyCO ~ rRH + 1, data = CO_hour7160)
summary(model7160hcoRH)
```

sensor 7160; daily
```{r}
temp3 <- airly_co %>%
  filter(sensor_id == '7160') %>%
  group_by(day) %>%
  summarise(adailyCO = mean(CO, na.rm = T))
CO_day7160 <- merge(temp3, temp4, by = "day") %>%
  mutate(new_adailyCO = adailyCO * 8.314 * (rTemp+273.15)/(rPre*100*28.01))
```

```{r}
CO_day7160 %>%
  ggplot(aes(day))+
  geom_line(aes(y=new_adailyCO, colour="airly"))+
  geom_line(aes(y=rdailyCO, colour="FRM"))+
  xlab("Date") +ylab("Daily CO [ppm]") +
  ggtitle('Sensor 7160')

model7160dco <- lm(new_adailyCO ~ rdailyCO + 1, data = CO_day7160)
summary(model7160dco)
model7160dcoTRH <- lm(new_adailyCO ~ rdailyCO + rTemp + rRH + 1, data = CO_day7160)
summary(model7160dcoTRH)
model7160dcoT <- lm(new_adailyCO ~ rTemp + 1, data = CO_day7160)
summary(model7160dcoT)
model7160dcoRH <- lm(new_adailyCO ~ rRH+ 1, data = CO_day7160)
summary(model7160dcoRH)
```

sensor 7205; hourly
```{r}
temp1 <- airly_co %>%
  filter(sensor_id == '7205') %>%
  group_by(dayhour) %>%
  summarise(ahourlyCO = mean(CO, na.rm = T))
CO_hour7205 <- merge(temp1, temp2, by = "dayhour") %>%
  mutate(new_ahourlyCO = ahourlyCO * 8.314 * (rTemp+273.15)/(rPre*100*28.01))
#unit of rTemp is degree celsius; unit of rPre is mbar which is 100pa
```

```{r}
CO_hour7205 %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=new_ahourlyCO, colour="Airly"))+
  geom_line(aes(y=rhourlyCO, colour="FRM"))+
  xlab("Date") +ylab("hourly CO [ppm]") +
  ggtitle('Sensor 7205')
CO_7205

model7205hco <- lm(new_ahourlyCO ~ rhourlyCO + 1, data = CO_hour7205)
summary(model7205hco)

model7205hcoTRH <- lm(new_ahourlyCO ~ rhourlyCO + rTemp + rRH + 1, data = CO_hour7205)
summary(model7205hcoTRH)

model7205hcoT <- lm(new_ahourlyCO ~ rTemp + 1, data = CO_hour7160)
summary(model7205hcoT)
model7205hcoRH <- lm(new_ahourlyCO ~ rRH + 1, data = CO_hour7160)
summary(model7205hcoRH)
```

sensor 7205; daily
```{r}
temp3 <- airly_co %>%
  filter(sensor_id == '7205') %>%
  group_by(day) %>%
  summarise(adailyCO = mean(CO, na.rm = T))
CO_day7205 <- merge(temp3, temp4, by = "day") %>%
  mutate(new_adailyCO = adailyCO * 8.314 * (rTemp+273.15)/(rPre*100*28.01))
```

```{r}
CO_day7205 %>%
  ggplot(aes(day))+
  geom_line(aes(y=new_adailyCO, colour="airly"))+
  geom_line(aes(y=rdailyCO, colour="FRM"))+
  xlab("Date") +ylab("Daily CO [ppm]") +
  ggtitle('Sensor 7205')

model7205dco <- lm(new_adailyCO ~ rdailyCO + 1, data = CO_day7205)
summary(model7205dco)

model7205dcoTRH <- lm(new_adailyCO ~ rdailyCO + rTemp + rRH + 1, data = CO_day7205)
summary(model7205dcoTRH)
model7205dcoT <- lm(new_adailyCO ~ rTemp + 1, data = CO_day7160)
summary(model7205dcoT)
model7205dcoRH <- lm(new_adailyCO ~ rRH+ 1, data = CO_day7160)
summary(model7205dcoRH)
```

sensor 7250; hourly
```{r}
temp1 <- airly_co %>%
  filter(sensor_id == '7250') %>%
  group_by(dayhour) %>%
  summarise(ahourlyCO = mean(CO, na.rm = T))
CO_hour7250 <- merge(temp1, temp2, by = "dayhour") %>%
  mutate(new_ahourlyCO = ahourlyCO * 8.314 *           (rTemp+273.15)/(rPre*100*28.01))
#unit of rTemp is degree celsius; unit of rPre is mbar which is 100pa
```

```{r}
CO_hour7250 %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=new_ahourlyCO, colour="airly"))+
  geom_line(aes(y=rhourlyCO, colour="regular"))+
  xlab("Date") +ylab("hourly CO [ppm]") +
  ggtitle('Sensor 7250')
model7250hco <- lm(new_ahourlyCO ~ rhourlyCO + 1, data = CO_hour7250)
summary(model7250hco)
model7250hcoTRH <- lm(new_ahourlyCO ~ rhourlyCO + rTemp + rRH + 1, data = CO_hour7250)
summary(model7250hcoTRH)
model7250hcoT <- lm(new_ahourlyCO ~ rTemp + 1, data = CO_hour7160)
summary(model7250hcoT)
model7250hcoRH <- lm(new_ahourlyCO ~ rRH + 1, data = CO_hour7160)
summary(model7250hcoRH)
```

sensor 7250; daily
```{r}
temp3 <- airly_co %>%
  filter(sensor_id == '7250') %>%
  group_by(day) %>%
  summarise(adailyCO = mean(CO, na.rm = T))
CO_day7250 <- merge(temp3, temp4, by = "day") %>%
  mutate(new_adailyCO = adailyCO * 8.314 * (rTemp+273.15)/(rPre*100*28.01))
```

```{r}
CO_day7250 %>%
  ggplot(aes(day))+
  geom_line(aes(y=new_adailyCO, colour="airly"))+
  geom_line(aes(y=rdailyCO, colour="FRM"))+
  xlab("Date") +ylab("Daily CO [ppm]") +
  ggtitle('Sensor 7250')

model7250dco <- lm(new_adailyCO ~ rdailyCO + 1, data = CO_day7250)
summary(model7250dco)

model7250dcoTRH <- lm(new_adailyCO ~ rdailyCO + rTemp + rRH + 1, data = CO_day7250)
summary(model7250dcoTRH)
model7250dcoT <- lm(new_adailyCO ~ rTemp + 1, data = CO_day7160)
summary(model7250dcoT)
model7250dcoRH <- lm(new_adailyCO ~ rRH+ 1, data = CO_day7160)
summary(model7250dcoRH)
```

save hourly regression models to use in another R session
```{r}
save(model7160hco, model7205hco, model7250hco, file = "hourlyco.RData")
save(model7160dco, model7205dco, model7250dco, file = "Dailyco.RData")
```

hourly sensor to sensor comparison
```{r}
CO_7160h <- CO_hour7160 %>%
  mutate(corrected_CO = (new_ahourlyCO - coef(model7160hcoTRH)[1][1] - rTemp * coef(model7160hcoTRH)[3][1] - rRH * coef(model7160hcoTRH)[4][1])/coef(model7160hcoTRH)[2][1])
CO_7205h <- CO_hour7205 %>%
  mutate(corrected_CO = (new_ahourlyCO - coef(model7205hcoTRH)[1][1] - rTemp * coef(model7205hcoTRH)[3][1] - rRH * coef(model7205hcoTRH)[4][1])/coef(model7205hcoTRH)[2][1])
CO_7250h <- CO_hour7250 %>%
  mutate(corrected_CO = (new_ahourlyCO - coef(model7250hcoTRH)[1][1] - rTemp * coef(model7250hcoTRH)[3][1] - rRH * coef(model7250hcoTRH)[4][1])/coef(model7250hcoTRH)[2][1])
CO_7160h$sensor_id <- '7160'
CO_7205h$sensor_id <- '7205'
CO_7250h$sensor_id <- '7250' 

correct_vis <- rbind(CO_7160h, CO_7205h, CO_7250h)%>%
  select(dayhour, corrected_CO, sensor_id)
regularCOh <- CO_7160h %>% select(dayhour, rhourlyCO)
regularCOh$sensor_id <- 'FRM/FEM'

coh_sensortosensor_c <- ggplot(data = correct_vis, aes(x=dayhour, y=corrected_CO)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = regularCOh, aes(x=dayhour, y=rhourlyCO, lty="FRM/FEM"), color="black") +
  xlab("Hour") +ylab("") + ggtitle('After Correction')
#ggsave("coh_sensortosensor_c.png")
```

```{r}
correct_vis <- rbind(CO_7160h, CO_7205h, CO_7250h)%>%
  mutate(hour = hour(strptime(dayhour, format="%Y-%m-%d %H:%M:%S"))) %>%
  select(hour, corrected_CO, sensor_id) %>%
  group_by(hour, sensor_id) %>%
  summarise(hourlyCO = mean(corrected_CO, na.rm = T)) %>%
  na.omit()

regularCOh <- CO_7160h %>%
  mutate(hour = hour(strptime(dayhour, format="%Y-%m-%d %H:%M:%S"))) %>%
  select(hour, rhourlyCO) %>%
  group_by(hour) %>%
  summarise(hourlyCO = mean(rhourlyCO, na.rm = T))
regularCOh$sensor_id <- 'FRM/FEM'

coh_pattern_c <- ggplot(data = correct_vis, aes(x=hour, y=hourlyCO)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = regularCOh, aes(x=hour, y=hourlyCO, lty="FRM/FEM"), color="black")  +
  ggtitle("CO")+
  xlab("Hour") +ylab("Hourly CO [ppm]")
```


daily sensor to sensor comparison
```{r}
CO_7160d <- CO_day7160 %>%
  mutate(corrected_CO = (new_adailyCO - coef(model7160dcoTRH)[1][1] - rTemp * coef(model7160dcoTRH)[3][1] - rRH * coef(model7160dcoTRH)[4][1])/coef(model7160dcoTRH)[2][1])
CO_7205d <- CO_day7205 %>%
  mutate(corrected_CO = (new_adailyCO - coef(model7205dcoTRH)[1][1] - rTemp * coef(model7205dcoTRH)[3][1] - rRH * coef(model7205dcoTRH)[4][1])/coef(model7205dcoTRH)[2][1])
CO_7250d <- CO_day7250 %>%
  mutate(corrected_CO = (new_adailyCO - coef(model7250dcoTRH)[1][1] - rTemp * coef(model7250dcoTRH)[3][1] - rRH * coef(model7250dcoTRH)[4][1])/coef(model7250dcoTRH)[2][1])
CO_7160d$sensor_id <- '7160'
CO_7205d$sensor_id <- '7205'
CO_7250d$sensor_id <- '7250' 

correct_vis <- rbind(CO_7160d, CO_7205d, CO_7250d)%>%
  select(day, corrected_CO, sensor_id)
regularCOday <- CO_7160d %>% select(day, rdailyCO)
regularCOday$sensor_id <- 'FRM/FEM'

cod_sensortosensor_c <- ggplot(data = correct_vis, aes(x=day, y=corrected_CO)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = regularCOday, aes(x=day, y=rdailyCO, lty="FRM/FEM"), color="black") +
  xlab("Date") +ylab("") + ggtitle('After Correction')
#ggsave("cod_sensortosensor_c.png")
```



```{r}
r1 <- ggplot(model7160day1, aes(x = rdailyCO, y = new_adailyCO)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 0.1, label.y = 0.9, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 0.1, label.y = 0.8, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  xlab("FRM/FEM CO [ppm]") +ylab("Daily CO [ppm]")
r2 <- ggplot(model7205day1, aes(x = rdailyCO, y = new_adailyCO)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
 stat_regline_equation(label.x = 0.1, label.y = 0.9, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 0.1, label.y = 0.8, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  xlab("FRM/FEM CO [ppm]") +ylab("Daily CO [ppm]")
r3 <- ggplot(model7250day1, aes(x = rdailyCO, y = new_adailyCO)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 0.1, label.y = 0.9, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 0.1, label.y = 0.8, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 1), ylim = c(0, 1)) +
  xlab("FRM/FEM CO [ppm]") +ylab("Daily CO [ppm]")
ggarrange(r1, r2, r3,
          labels = c("Airly 7160", "Airly 7205", "Airly 7250"), hjust = 0.005,
          ncol = 2, nrow = 2)
```

