---
title: "PM2.5"
author: "Siyan Pu"
date: "11/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(dplyr)
library(tidyr)
library(lubridate)
library(ggplot2)
library(ggpubr)

library(httr)
library(jsonlite)
```


airly all pm2.5 data preprocessing
```{r}
airly_pm25b <- read.csv("airly_pm25.csv", check.names = F)
airly_pm25b <- airly_pm25b %>%
  gather(sensor_id, pm25, -c('Time')) %>%
  rename('date' = 'Time')
airly_pm25b <- airly_pm25b[,c(1,3,2)]
airly_pm25b$sensor_id <- as.integer(airly_pm25b$sensor_id)

airly_pm25c <- read.csv("airly_pm25_nov.csv", check.names = F)
airly_pm25c <- airly_pm25c %>%
  gather(sensor_id, pm25, -c('Time', 'mark')) %>%
  rename('date' = 'Time')
airly_pm25c$sensor_id <- as.integer(airly_pm25c$sensor_id)

airly_pm25c <- airly_pm25c %>%
  select(-mark)
airly_pm25c <- airly_pm25c[,c(1,3,2)]
```

```{r}
airly1_pm25a <- read.csv("airly1.csv") %>%
  select(date, pm25, sensor_id)
airly1 <- rbind(airly1_pm25a, airly_pm25b, airly_pm25c)
#convert to EST time zone (before daylight saving, 7 hour difference)
#convert to EST time zone (after daylight saving, starting on Oct. 31 02:25, 6 hour difference)
airly1$time <- as.POSIXct(airly1$date, format="%Y-%m-%d %H:%M:%S", tz="CET")
airly1$time <- lubridate::with_tz(airly1$time, "EST")
airly1$day <- date(strptime(airly1$time, format="%Y-%m-%d %H:%M:%S"))
airly1$hour <- hour(strptime(airly1$time, format="%Y-%m-%d %H:%M:%S"))

airly1$dayhour <- lubridate::ymd_h(format(as.POSIXct(airly1$time,format="%Y-%m-%d %H:%M:%S"),"%Y-%m-%d %H"))
airly1$sensor_id <- as.factor(airly1$sensor_id)
airly1pm25 <- airly1 %>%
  filter(day >= '2021-09-06' & day <= '2021-11-07')
```

Precision for PM2.5
```{r}
temp1 <- airly1 %>%
  group_by(day) %>%
  summarise(dailyPM25_all = mean(pm25, na.rm = T))

temp2 <- airly1 %>%
  group_by(day, sensor_id) %>%
  summarise(dailyPM25 = mean(pm25, na.rm = T))

PM25 <- merge(temp1, temp2, by = "day", all.x = T) %>%
  mutate(diff_square = (dailyPM25_all-dailyPM25)**2)

M <- n_distinct(PM25$sensor_id)
N <- n_distinct(PM25$day)

SD <- sqrt(sum(PM25$diff_square, na.rm=T) / (M*N-1))
SD/mean(airly1$pm25, na.rm=T)*100
```


```{r}
regular_pm25a <- regular1 %>%
  group_by(day) %>%
  summarise(rdailyPM25 = mean(PM25, na.rm = T))

regular_pm25b <- regular2 %>%
  group_by(day) %>%
  summarise(rdailyPM25 = mean(PM25, na.rm = T))

temp2 <- rbind(regular_pm25a, regular_pm25b) 
```

```{r}
temp3 <- rbind(regular1 %>%
  group_by(dayhour) %>%
  summarise(rhourlyPM25 = mean(PM25, na.rm = T)), regular2 %>%
  group_by(dayhour) %>%
  summarise(rhourlyPM25 = mean(PM25, na.rm = T)))
#divide pm2.5 hourly concentrations into quarters
threshold1 <- (max(temp3$rhourlyPM25) - min(temp3$rhourlyPM25))/4 + min(temp3$rhourlyPM25)
threshold2 <- 2 * (max(temp3$rhourlyPM25) - min(temp3$rhourlyPM25))/4 + min(temp3$rhourlyPM25)
threshold3 <- 3 * (max(temp3$rhourlyPM25) - min(temp3$rhourlyPM25))/4 + min(temp3$rhourlyPM25)
```

RMSE for PM2.5
```{r}
temp1 <- airly1 %>%
  group_by(day, sensor_id) %>%
  summarise(dailyPM25 = mean(pm25, na.rm = T))

PM25 <- merge(temp1, temp2, by = "day", all.x = T)  %>%
  na.omit() %>%
  mutate(diff_square = (rdailyPM25-dailyPM25)**2)

M <- n_distinct(PM25$sensor_id)
N <- n_distinct(PM25$day)

RMSE <- sqrt(sum(PM25$diff_square)/(M*N))
RMSE/mean(temp2$rdailyPM25, na.rm=T)*100

#Accuracy
100-(mean(airly1$pm25, na.rm = T)-mean(temp2$rdailyPM25, na.rm = T))/mean(temp2$rdailyPM25, na.rm = T)*100

#Inter-sensor Variability
sensor_avg <- airly1 %>%
  group_by(sensor_id) %>%
  summarise(avge = mean(pm25, na.rm = T)) %>%
  arrange(avge)

(max(sensor_avg$avge)-min(sensor_avg$avge))/mean(sensor_avg$avge, na.rm=T)
```

sensor to sensor comparison plot (daily)
```{r}
temp1 <- airly1pm25 %>%
  group_by(day, sensor_id) %>%
  summarise(dailyPM25 = mean(pm25, na.rm = T)) %>%
  na.omit()

temp2 <- rbind(regular1 %>%
  group_by(day) %>%
  summarise(dailyPM25 = mean(PM25, na.rm = T)), regular2 %>%
  group_by(day) %>%
  summarise(dailyPM25 = mean(PM25, na.rm = T)))
temp2$sensor_id <- 'FRM'


pm25d_sensortosensor <- ggplot(data = temp1, aes(x=day, y=dailyPM25)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = temp2, aes(x=day, y=dailyPM25, lty="FRM/FEM"), color="black") +
  xlab("Date") +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Before Correction')
#ggsave("pm25d_sensortosensor.png")
```

  
sensor to sensor comparison plot (hourly)
```{r}
temp1 <- airly1pm25 %>%
  group_by(dayhour, sensor_id) %>%
  summarise(hourlyPM25 = mean(pm25, na.rm = T)) %>%
  na.omit()

temp2 <- rbind(regular1 %>%
  group_by(dayhour) %>%
  summarise(hourlyPM25 = mean(PM25, na.rm = T)), regular2 %>%
  group_by(dayhour) %>%
  summarise(hourlyPM25 = mean(PM25, na.rm = T)))
temp2$sensor_id <- 'FRM'


pm25h_sensortosensor <- ggplot(data = temp1 , aes(x=dayhour, y=hourlyPM25)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = temp2, aes(x=dayhour, y=hourlyPM25, lty="FRM/FEM"), color="black") +
  xlab("Hour") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Before Correction')
#ggsave("pm25h_sensortosensor.png")
```

observe diurnal pattern
```{r}
temp1 <- airly1pm25 %>%
  group_by(hour, sensor_id) %>%
  summarise(hourlyPM25 = mean(pm25, na.rm = T)) %>%
  na.omit()

temp2 <- rbind(regular1, regular2) %>%
  group_by(hour) %>%
  summarise(hourlyPM25 = mean(PM25, na.rm = T))
temp2$sensor_id <- 'FRM'

pm25h_pattern <- ggplot(data = temp1 , aes(x=hour, y=hourlyPM25)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = temp2, aes(x=hour, y=hourlyPM25, lty="FRM/FEM"), color="black") +
  ggtitle(expression(paste("P", M[2.5])))+
  xlab("Hour") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
```



multiple sensors regression model graphing
```{r}
temp1 <- airly1 %>%
  group_by(day, sensor_id) %>%
  summarise(dailyPM25 = mean(pm25, na.rm = T)) %>%
  na.omit()

PM25 <- merge(temp1, temp2, by="day", all.x = T)
ggplot(PM25, aes(x=rdailyPM25, y=dailyPM25, col=sensor_id)) + geom_point() +
            geom_smooth(method="lm", se=FALSE)
```

```{r}
regular_pm25a <- regular1 %>%
  group_by(day) %>%
  summarise(rdailyPM25 = mean(PM25, na.rm = T))

regular_pm25b <- regular2 %>%
  group_by(day) %>%
  summarise(rdailyPM25 = mean(PM25, na.rm = T))

temp2 <- rbind(regular_pm25a, regular_pm25b)
```

'7160' daily
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7160') %>%
  group_by(day) %>%
  summarise(adailyPM25 = mean(pm25, na.rm = T))
#temp1$pm25level <- as.numeric(cut2(temp1$pm25, g=4))
merge(temp1, temp2, by = "day") %>%
  ggplot(aes(day))+
  geom_line(aes(y=adailyPM25, colour="Airly"))+
  geom_line(aes(y=rdailyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7160')

PM25_day <- merge(temp1, temp2, by = "day")
cor(PM25_day$adailyPM25, PM25_day$rdailyPM25)
model7160dpm25 <- lm(adailyPM25 ~ rdailyPM25 + 1, data = PM25_day)
summary(model7160dpm25)
PM25_7160d <- PM25_day %>%
  mutate(corrected_PM25 = (adailyPM25 - coef(model7160dpm25)[1][1]) / coef(model7160dpm25)[2][1])
```

7160 hourly
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7160') %>%
  group_by(dayhour) %>%
  summarise(ahourlyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp3, by = "dayhour") %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=ahourlyPM25, colour="Airly"))+
  geom_line(aes(y=rhourlyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7160')

PM25_hour <- merge(temp1, temp3, by = "dayhour")
cor(PM25_hour$ahourlyPM25, PM25_hour$rhourlyPM25)
model7160hpm25 <- lm(ahourlyPM25 ~ rhourlyPM25 + 1, data = PM25_hour)
summary(model7160hpm25)
PM25_7160h <- PM25_hour %>%
  mutate(corrected_PM25 = (ahourlyPM25 - coef(model7160hpm25)[1][1]) / coef(model7160hpm25)[2][1])
```

'7194' daily
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7194') %>%
  group_by(day) %>%
  summarise(adailyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp2, by = "day") %>%
  ggplot(aes(day))+
  geom_line(aes(y=adailyPM25, colour="Airly"))+
  geom_line(aes(y=rdailyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7194')

PM25_day <- merge(temp1, temp2, by = "day")
cor(PM25_day$adailyPM25, PM25_day$rdailyPM25)
model7194dpm25 <- lm(adailyPM25 ~ rdailyPM25 + 1, data = PM25_day)
summary(model7194dpm25)
PM25_7194d <- PM25_day %>%
  mutate(corrected_PM25 = (adailyPM25 - coef(model7194dpm25)[1][1]) / coef(model7194dpm25)[2][1])
```

7194 hourly
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7194') %>%
  group_by(dayhour) %>%
  summarise(ahourlyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp3, by = "dayhour") %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=ahourlyPM25, colour="Airly"))+
  geom_line(aes(y=rhourlyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7194')

PM25_hour <- merge(temp1, temp3, by = "dayhour")
cor(PM25_hour$ahourlyPM25, PM25_hour$rhourlyPM25)
model7194hpm25 <- lm(ahourlyPM25 ~ rhourlyPM25 + 1, data = PM25_hour)
summary(model7194hpm25)
PM25_7194h <- PM25_hour %>%
  mutate(corrected_PM25 = (ahourlyPM25 - coef(model7194hpm25)[1][1]) / coef(model7194hpm25)[2][1])
```

'7205' daily
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7205') %>%
  group_by(day) %>%
  summarise(adailyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp2, by = "day") %>%
  ggplot(aes(day))+
  geom_line(aes(y=adailyPM25, colour="Airly"))+
  geom_line(aes(y=rdailyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7205')

PM25_day <- merge(temp1, temp2, by = "day")
cor(PM25_day$adailyPM25, PM25_day$rdailyPM25)
model7205dpm25 <- lm(adailyPM25 ~ rdailyPM25 + 1, data = PM25_day)
summary(model7205dpm25)
PM25_7205d <- PM25_day %>%
  mutate(corrected_PM25 = (adailyPM25 - coef(model7205dpm25)[1][1]) / coef(model7205dpm25)[2][1])
```


7205 hourly
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7205') %>%
  group_by(dayhour) %>%
  summarise(ahourlyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp3, by = "dayhour") %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=ahourlyPM25, colour="Airly"))+
  geom_line(aes(y=rhourlyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7205')

PM25_hour <- merge(temp1, temp3, by = "dayhour")
cor(PM25_hour$ahourlyPM25, PM25_hour$rhourlyPM25)
model7205hpm25 <- lm(ahourlyPM25 ~ rhourlyPM25 + 1, data = PM25_hour)
summary(model7205hpm25)
PM25_7205h <- PM25_hour %>%
  mutate(corrected_PM25 = (ahourlyPM25 - coef(model7205hpm25)[1][1]) / coef(model7205hpm25)[2][1])
```

'7250' daily
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7250') %>%
  group_by(day) %>%
  summarise(adailyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp2, by = "day") %>%
  ggplot(aes(day))+
  geom_line(aes(y=adailyPM25, colour="Airly"))+
  geom_line(aes(y=rdailyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7250')

PM25_day <- merge(temp1, temp2, by = "day")
cor(PM25_day$adailyPM25, PM25_day$rdailyPM25)
model7250dpm25 <- lm(adailyPM25 ~ rdailyPM25 + 1, data = PM25_day)
summary(model7250dpm25)
PM25_7250d <- PM25_day %>%
  mutate(corrected_PM25 = (adailyPM25 - coef(model7250dpm25)[1][1]) / coef(model7250dpm25)[2][1])
```

7250 hourly
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7250') %>%
  group_by(dayhour) %>%
  summarise(ahourlyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp3, by = "dayhour") %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=ahourlyPM25, colour="Airly"))+
  geom_line(aes(y=rhourlyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7250')

PM25_hour <- merge(temp1, temp3, by = "dayhour")
cor(PM25_hour$ahourlyPM25, PM25_hour$rhourlyPM25)
model7250hpm25 <- lm(ahourlyPM25 ~ rhourlyPM25 + 1, data = PM25_hour)
summary(model7250hpm25)
PM25_7250h <- PM25_hour %>%
  mutate(corrected_PM25 = (ahourlyPM25 - coef(model7250hpm25)[1][1]) / coef(model7250hpm25)[2][1])
```

'7276' daily
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7276') %>%
  group_by(day) %>%
  summarise(adailyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp2, by = "day") %>%
  ggplot(aes(day))+
  geom_line(aes(y=adailyPM25, colour="Airly"))+
  geom_line(aes(y=rdailyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7276')

PM25_day <- merge(temp1, temp2, by = "day")
cor(PM25_day$adailyPM25, PM25_day$rdailyPM25)
model7276dpm25 <- lm(adailyPM25 ~ rdailyPM25 + 1, data = PM25_day)
summary(model7276dpm25)
PM25_7276d <- PM25_day %>%
  mutate(corrected_PM25 = (adailyPM25 - coef(model7276dpm25)[1][1]) / coef(model7276dpm25)[2][1])
```


7276 hourly
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7276') %>%
  group_by(dayhour) %>%
  summarise(ahourlyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp3, by = "dayhour") %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=ahourlyPM25, colour="Airly"))+
  geom_line(aes(y=rhourlyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7276')

PM25_hour <- merge(temp1, temp3, by = "dayhour")
cor(PM25_hour$ahourlyPM25, PM25_hour$rhourlyPM25)
model7276hpm25 <- lm(ahourlyPM25 ~ rhourlyPM25 + 1, data = PM25_hour)
summary(model7276hpm25)
PM25_7276h <- PM25_hour %>%
  mutate(corrected_PM25 = (ahourlyPM25 - coef(model7276hpm25)[1][1]) / coef(model7276hpm25)[2][1])
```

'7284' daily
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7284') %>%
  group_by(day) %>%
  summarise(adailyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp2, by = "day") %>%
  ggplot(aes(day))+
  geom_line(aes(y=adailyPM25, colour="Airly"))+
  geom_line(aes(y=rdailyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7284')

PM25_day <- merge(temp1, temp2, by = "day")
cor(PM25_day$adailyPM25, PM25_day$rdailyPM25)
model7284dpm25 <- lm(adailyPM25 ~ rdailyPM25 + 1, data = PM25_day)
summary(model7284dpm25)
PM25_7284d <- PM25_day %>%
  mutate(corrected_PM25 = (adailyPM25 - coef(model7284dpm25)[1][1]) / coef(model7284dpm25)[2][1])
```


7284 hourly
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7284') %>%
  group_by(dayhour) %>%
  summarise(ahourlyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp3, by = "dayhour") %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=ahourlyPM25, colour="Airly"))+
  geom_line(aes(y=rhourlyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7284')

PM25_hour <- merge(temp1, temp3, by = "dayhour")
cor(PM25_hour$ahourlyPM25, PM25_hour$rhourlyPM25)
model7284hpm25 <- lm(ahourlyPM25 ~ rhourlyPM25 + 1, data = PM25_hour)
summary(model7284hpm25)
PM25_7284h <- PM25_hour %>%
  mutate(corrected_PM25 = (ahourlyPM25 - coef(model7284hpm25)[1][1]) / coef(model7284hpm25)[2][1])
```

'7304' daily
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7304') %>%
  group_by(day) %>%
  summarise(adailyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp2, by = "day") %>%
  ggplot(aes(day))+
  geom_line(aes(y=adailyPM25, colour="Airly"))+
  geom_line(aes(y=rdailyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7304')

PM25_day <- merge(temp1, temp2, by = "day")
cor(PM25_day$adailyPM25, PM25_day$rdailyPM25)
model7304dpm25 <- lm(adailyPM25 ~ rdailyPM25 + 1, data = PM25_day)
summary(model7304dpm25)
PM25_7304d <- PM25_day %>%
  mutate(corrected_PM25 = (adailyPM25 - coef(model7304dpm25)[1][1]) / coef(model7304dpm25)[2][1])
```


7304 hourly
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7304') %>%
  group_by(dayhour) %>%
  summarise(ahourlyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp3, by = "dayhour") %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=ahourlyPM25, colour="Airly"))+
  geom_line(aes(y=rhourlyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7304')

PM25_hour <- merge(temp1, temp3, by = "dayhour")
cor(PM25_hour$ahourlyPM25, PM25_hour$rhourlyPM25)
model7304hpm25 <- lm(ahourlyPM25 ~ rhourlyPM25 + 1, data = PM25_hour)
summary(model7304hpm25)
PM25_7304h <- PM25_hour %>%
  mutate(corrected_PM25 = (ahourlyPM25 - coef(model7304hpm25)[1][1]) / coef(model7304hpm25)[2][1])
```

'7396'  daily (seems there is an outlier)
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7396') %>%
  group_by(day) %>%
  summarise(adailyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp2, by = "day") %>%
  ggplot(aes(day))+
  geom_line(aes(y=adailyPM25, colour="Airly"))+
  geom_line(aes(y=rdailyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7396')

PM25_day <- merge(temp1, temp2, by = "day")
cor(PM25_day$adailyPM25, PM25_day$rdailyPM25)
model7396dpm25 <- lm(adailyPM25 ~ rdailyPM25 + 1, data = PM25_day)
summary(model7396dpm25)
PM25_7396d <- PM25_day %>%
  mutate(corrected_PM25 = (adailyPM25 - coef(model7396dpm25)[1][1]) / coef(model7396dpm25)[2][1])
```

7396 hourly
```{r}
temp1 <- airly1pm25 %>%
  filter(sensor_id == '7396') %>%
  group_by(dayhour) %>%
  summarise(ahourlyPM25 = mean(pm25, na.rm = T))

merge(temp1, temp3, by = "dayhour") %>%
  ggplot(aes(dayhour))+
  geom_line(aes(y=ahourlyPM25, colour="Airly"))+
  geom_line(aes(y=rhourlyPM25, colour="FRM"))+
  xlab("Date") +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]"))) + ggtitle('Sensor 7396')

PM25_hour <- merge(temp1, temp3, by = "dayhour")
cor(PM25_hour$ahourlyPM25, PM25_hour$rhourlyPM25)
model7396hpm25 <- lm(ahourlyPM25 ~ rhourlyPM25 + 1, data = PM25_hour)
summary(model7396hpm25)
PM25_7396h <- PM25_hour %>%
  mutate(corrected_PM25 = (ahourlyPM25 - coef(model7396hpm25)[1][1]) / coef(model7396hpm25)[2][1])
```

save hourly and daily regression models to use in another R session
```{r}
save(model7160hpm25, model7194hpm25, model7205hpm25, model7250hpm25, model7276hpm25, model7284hpm25, model7304hpm25, model7396hpm25, file = "hourlypm25.RData")
save(model7160dpm25, model7194dpm25, model7205dpm25, model7250dpm25, model7276dpm25, model7284dpm25, model7304dpm25, model7396dpm25, file = "Dailypm25.RData")
```


daily time series for corrected data
```{r}
PM25_7160d$sensor_id <- '7160'
PM25_7194d$sensor_id <- '7194'
PM25_7205d$sensor_id <- '7205'
PM25_7250d$sensor_id <- '7250' 
PM25_7276d$sensor_id <- '7276'
PM25_7284d$sensor_id <- '7284'
PM25_7304d$sensor_id <- '7304'
PM25_7396d$sensor_id <- '7396'

correct_vis <- rbind(PM25_7160d, PM25_7194d, PM25_7205d, PM25_7250d, PM25_7276d, PM25_7284d, PM25_7304d, PM25_7396d)%>%
  select(day, corrected_PM25, sensor_id)
regularPM25day <- PM25_7160d %>% select(day, rdailyPM25)
regularPM25day$sensor_id <- 'FRM/FEM'

pm25d_sensortosensor_c <- ggplot(data = correct_vis, aes(x=day, y=corrected_PM25)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = regularPM25day, aes(x=day, y=rdailyPM25, lty="FRM/FEM"), color="black") +
  xlab("Date") +ylab("") + ggtitle('After Correction')
#ggsave("pm25d_sensortosensor_c.png")
```

hourly time series for corrected data
```{r}
PM25_7160h$sensor_id <- '7160'
PM25_7194h$sensor_id <- '7194'
PM25_7205h$sensor_id <- '7205'
PM25_7250h$sensor_id <- '7250' 
PM25_7276h$sensor_id <- '7276'
PM25_7284h$sensor_id <- '7284'
PM25_7304h$sensor_id <- '7304'
PM25_7396h$sensor_id <- '7396'

correct_vis <- rbind(PM25_7160h, PM25_7194h, PM25_7205h, PM25_7250h, PM25_7276h, PM25_7284h, PM25_7304h, PM25_7396h)%>%
  select(dayhour, corrected_PM25, sensor_id)
regularPM25h <- PM25_7160h %>% select(dayhour, rhourlyPM25)
regularPM25h$sensor_id <- 'FRM/FEM'

pm25h_sensortosensor_c <- ggplot(data = correct_vis, aes(x=dayhour, y=corrected_PM25)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = regularPM25h, aes(x=dayhour, y=rhourlyPM25, lty="FRM/FEM"), color="black") +
  xlab("Hour") +ylab("") + ggtitle('After Correction')
#ggsave("pm25h_sensortosensor_c.png")
```

diurnal pattern after correction
```{r}
PM25_7160h$sensor_id <- '7160'
PM25_7194h$sensor_id <- '7194'
PM25_7205h$sensor_id <- '7205'
PM25_7250h$sensor_id <- '7250' 
PM25_7276h$sensor_id <- '7276'
PM25_7284h$sensor_id <- '7284'
PM25_7304h$sensor_id <- '7304'
PM25_7396h$sensor_id <- '7396'

correct_vis <- rbind(PM25_7160h, PM25_7194h, PM25_7205h, PM25_7250h, PM25_7276h, PM25_7284h, PM25_7304h, PM25_7396h)%>%
  mutate(hour = hour(strptime(dayhour, format="%Y-%m-%d %H:%M:%S"))) %>%
  select(hour, corrected_PM25, sensor_id) %>%
  group_by(hour, sensor_id) %>%
  summarise(hourlyPM25 = mean(corrected_PM25, na.rm = T)) %>%
  na.omit()

regularPM25h <- PM25_7160h %>%
  mutate(hour = hour(strptime(dayhour, format="%Y-%m-%d %H:%M:%S"))) %>%
  select(hour, rhourlyPM25) %>%
  group_by(hour) %>%
  summarise(hourlyPM25 = mean(rhourlyPM25, na.rm = T))
regularPM25h$sensor_id <- 'FRM/FEM'

pm25h_pattern_c <- ggplot(data = correct_vis, aes(x=hour, y=hourlyPM25)) + geom_line(aes(col=sensor_id)) +
  geom_line(data = regularPM25h, aes(x=hour, y=hourlyPM25, lty="FRM/FEM"), color="black") +
  ggtitle(expression(paste("P", M[2.5]))) +
  xlab("Hour") + ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
```

regression graphs for 8 sensors
```{r}
#par(mfcol = c(2, 2))
r1 <- ggplot(model7160dpm25, aes(x = rdailyPM25, y = adailyPM25)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 15, label.y = 45, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 15, label.y = 40, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]")))
r2 <- ggplot(model7194dpm25, aes(x = rdailyPM25, y = adailyPM25)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 15, label.y = 45, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 15, label.y = 40, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]")))
r3 <- ggplot(model7205dpm25, aes(x = rdailyPM25, y = adailyPM25)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 15, label.y = 45, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 15, label.y = 40, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]")))
r4 <- ggplot(model7250dpm25, aes(x = rdailyPM25, y = adailyPM25)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 15, label.y = 45, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 15, label.y = 40, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]")))
r5 <- ggplot(model7276dpm25, aes(x = rdailyPM25, y = adailyPM25)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 15, label.y = 45, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 15, label.y = 40, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]")))
r6 <- ggplot(model7284dpm25, aes(x = rdailyPM25, y = adailyPM25)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 15, label.y = 45, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 15, label.y = 40, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]")))
r7 <- ggplot(model7304dpm25, aes(x = rdailyPM25, y = adailyPM25)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 15, label.y = 45, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 15, label.y = 40, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]")))
r8 <- ggplot(model7396dpm25, aes(x = rdailyPM25, y = adailyPM25)) + 
  geom_point() + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 15, label.y = 48, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 15, label.y = 44, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Daily P", M[2.5], " [",mu,"g ",m^-3,"]")))
ggarrange(r1, r2, r3, r4, 
          labels = c("Airly 7160", "Airly 7194", "Airly 7205", "Airly 7250"), hjust = 0.005,
          ncol = 2, nrow = 2)
ggarrange(r5, r6, r7, r8,
          labels = c("Airly 7276", "Airly 7284", "Airly 7304", "Airly 7396"),  hjust = 0.005,
          ncol = 2, nrow = 2)
```

hourly regression graphs for 8 sensors
```{r}
#par(mfcol = c(2, 2))
r1 <- ggplot(model7160hpm25, aes(x = rhourlyPM25, y = ahourlyPM25)) + 
  geom_point(alpha=0.3) + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 25, label.y = 15, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 25, label.y = 10, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
r2 <- ggplot(model7194hpm25, aes(x = rhourlyPM25, y = ahourlyPM25)) + 
  geom_point(alpha=0.3) + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 25, label.y = 15, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 25, label.y = 10, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
r3 <- ggplot(model7205hpm25, aes(x = rhourlyPM25, y = ahourlyPM25)) + 
  geom_point(alpha=0.3) + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 25, label.y = 15, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 25, label.y = 10, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
r4 <- ggplot(model7250hpm25, aes(x = rhourlyPM25, y = ahourlyPM25)) + 
  geom_point(alpha=0.3) + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 25, label.y = 15, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 25, label.y = 10, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
r5 <- ggplot(model7276hpm25, aes(x = rhourlyPM25, y = ahourlyPM25)) + 
  geom_point(alpha=0.3) + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 25, label.y = 15, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 25, label.y = 10, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
r6 <- ggplot(model7284hpm25, aes(x = rhourlyPM25, y = ahourlyPM25)) + 
  geom_point(alpha=0.3) + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 25, label.y = 15, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 25, label.y = 10, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
r7 <- ggplot(model7304hpm25, aes(x = rhourlyPM25, y = ahourlyPM25)) + 
  geom_point(alpha=0.3) + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 25, label.y = 15, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 25, label.y = 10, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
r8 <- ggplot(model7396hpm25, aes(x = rhourlyPM25, y = ahourlyPM25)) + 
  geom_point(alpha=0.3) + 
  geom_abline(linetype = "dashed", intercept = 0, slope = 1) +
  geom_smooth(method = "lm", se=FALSE) +
  stat_regline_equation(label.x = 25, label.y = 15, aes(label = ..eq.label..)) +
  stat_regline_equation(label.x = 25, label.y = 10, aes(label = ..adj.rr.label..)) +
  coord_fixed(xlim = c(0, 50), ylim = c(0, 50))+
  xlab(expression(paste("FRM/FEM P", M[2.5], " [",mu,"g ",m^-3,"]"))) +ylab(expression(paste("Hourly P", M[2.5], " [",mu,"g ",m^-3,"]")))
ggarrange(r1, r2, r3, r4, 
          labels = c("Airly 7160", "Airly 7194", "Airly 7205", "Airly 7250"), hjust = 0.005,
          ncol = 2, nrow = 2)
ggarrange(r5, r6, r7, r8,
          labels = c("Airly 7276", "Airly 7284", "Airly 7304", "Airly 7396"),  hjust = 0.005,
          ncol = 2, nrow = 2)
```

